% Manindra de Mel — resume
% Compile with: xelatex resume.tex   (run twice for hyperref refs)
%
% Editorial theme mirroring manindra-portfolio.web.app:
%   display = Helvetica Neue, mono = JetBrains Mono.
%   Falls back to Helvetica / DejaVu Sans Mono if those aren't installed.

\documentclass[10pt,a4paper]{extarticle}

\usepackage[a4paper, top=10mm, bottom=10mm, left=15mm, right=15mm]{geometry}
\usepackage{fontspec}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{microtype}
\usepackage[skip=2pt,indent=0pt]{parskip}
\usepackage[hidelinks]{hyperref}

%% ---- Fonts (graceful fallback) ----------------------------------------
\IfFontExistsTF{Helvetica Neue}
  {\setmainfont{Helvetica Neue}}
  {\IfFontExistsTF{Helvetica}
    {\setmainfont{Helvetica}}
    {\IfFontExistsTF{Inter}
      {\setmainfont{Inter}}
      {\IfFontExistsTF{Arial}
        {\setmainfont{Arial}}
        {\IfFontExistsTF{Segoe UI}
          {\setmainfont{Segoe UI}}
          {}}}}}

\IfFontExistsTF{JetBrains Mono}
  {\newfontfamily\monofont{JetBrains Mono}[Scale=0.92]}
  {\IfFontExistsTF{DejaVu Sans Mono}
    {\newfontfamily\monofont{DejaVu Sans Mono}[Scale=0.92]}
    {\IfFontExistsTF{Consolas}
      {\newfontfamily\monofont{Consolas}[Scale=0.92]}
      {\newfontfamily\monofont{Courier New}[Scale=0.92]}}}

%% ---- Colors ----------------------------------------------------------
\definecolor{ink}{HTML}{0a0a0a}
\definecolor{muted}{HTML}{6a6a6a}
\definecolor{rule}{HTML}{1a1a1a}
\color{ink}

%% ---- Helpers ---------------------------------------------------------
% Mono-caps ornamental label (used only for: dates, ¶ section markers, stack-table row labels)
\newcommand{\meta}[1]{{\monofont\addfontfeatures{LetterSpace=14.0}\scriptsize\textcolor{muted}{\MakeUppercase{#1}}}}
% Mono-caps inline label (stack table)
\newcommand{\monocaps}[1]{{\monofont\addfontfeatures{LetterSpace=8.0}\footnotesize\MakeUppercase{#1}}}
% Readable mono metadata (contact info, tech stacks, coursework — regular case, small but legible)
\newcommand{\detail}[1]{{\monofont\footnotesize\textcolor{muted}{#1}}}
% Right-aligned dates next to a heading
\newcommand{\dates}[1]{\hfill\meta{#1}}

% Editorial section header: ¶ NN — TITLE  + thin rule
\newcounter{secnum}
\newcommand{\edsection}[1]{%
  \stepcounter{secnum}%
  \par\vspace{5pt}%
  {\monofont\addfontfeatures{LetterSpace=18.0}\scriptsize\textcolor{muted}{¶ \ifnum\value{secnum}<10 0\fi\arabic{secnum}}}%
  \hspace{12pt}%
  {\bfseries\fontsize{14}{16}\selectfont\addfontfeatures{LetterSpace=-2.0}\MakeUppercase{#1}}%
  \par\vspace{1pt}%
  {\color{rule}\hrule height 0.5pt}%
  \par\vspace{2pt}%
}

% Tight bullet list
\setlist[itemize]{leftmargin=12pt, topsep=1pt, parsep=0pt, itemsep=1pt}
\renewcommand{\labelitemi}{\textcolor{muted}{\scriptsize\textbullet}}

\setlength{\parindent}{0pt}

\begin{document}

%% ---- Header ---------------------------------------------------------
{\fontsize{28}{30}\selectfont\bfseries\addfontfeatures{LetterSpace=-4.0}MANINDRA DE MEL\par}
\vspace{3pt}
\detail{Applied ML / Software Engineer — Canberra, AU}\par
\detail{manindrademel@yahoo.com.au · +61 498 842 763 · \href{https://manindra.com.au}{manindra.com.au}}\par
\detail{\href{https://github.com/ManindraDeMel}{github.com/ManindraDeMel} · \href{https://www.linkedin.com/in/manindra-de-mel-413a79160/}{linkedin.com/in/manindra-de-mel}}\par
\vspace{6pt}
{\color{rule}\hrule height 0.5pt}

%% ---- Summary --------------------------------------------------------
\edsection{Summary}
Build applied ML systems end-to-end — modeling, GPU data infrastructure, deployment. Recent focus on fine-grained vision with foundation models (BioCLIP, ViTs) and reinforcement learning for trading. Production-shipped backends and full-stack products for SMEs since 2021.

%% ---- Selected work --------------------------------------------------
\edsection{Selected Work}

{\bfseries PlantCLEF 2026 — Team Lead}\dates{2026 · 8th place, international}\par
\detail{w/ A. Sharma · R. Mistry · BioCLIP · PyTorch · NVIDIA DALI · cuDF · W\&B}\par
\begin{itemize}
\item Multi-label species ID across 7{,}800+ long-tailed classes on 1.4\,M quadrat-scale images.
\item Fine-tuned BioCLIP ViT-L/14 at 448\,px with bicubic-interpolated positional embeddings; asymmetric loss for extreme class imbalance.
\item End-to-end GPU pipeline (NVDEC → NVIDIA DALI + cuDF); SAHI-style 512$\times$512 tiled inference with max-pooled probabilities; rare-species recall tracked separately so the model couldn't coast on dominant classes.
\end{itemize}

\vspace{1pt}
{\bfseries Rocket Remit — Frontend Developer / Data Analyst}\dates{Aug 2023 — present}\par
\detail{TypeScript · React · Python · ML · SQL}\par
\begin{itemize}
\item Frontend work on the customer-facing remittance product; data analysis on transaction flows.
\item Built an ML transaction-monitoring system flagging suspicious activity patterns across remittance corridors — integrated into compliance review.
\end{itemize}

\vspace{1pt}
{\bfseries Purse — Founder / Engineer}\dates{2025 — present}\par
\detail{TypeScript · React Native · Firebase · CDR / Open Banking}\par
\begin{itemize}
\item Australian finance app: super, bank, and investments aggregated via Open Banking into one net-worth view; daily-spend feeds and budget envelopes with overshoot alerts — mobile-first, transactions auto-categorise on-device.
\end{itemize}

\vspace{1pt}
{\bfseries Stomble — Backend Engineer}\dates{Nov 2022 — May 2023}\par
\detail{Python · AWS · CI/CD}\par
\begin{itemize}
\item Led the backend team; designed services connecting native client apps to AWS-hosted infrastructure.
\item Owned AWS configuration, deployment, and operations; raised unit-test coverage and onboarded engineers.
\end{itemize}

\vspace{1pt}
{\bfseries OpenBMB · ChatDev — DevOps Contributor}\dates{2023}\par
\begin{itemize}
\item Contributed deployment and CI tooling to ChatDev — a multi-agent LLM software-development framework (\textgreater{}26k stars).
\end{itemize}

\vspace{1pt}
{\bfseries Freelance / sole trader}\dates{2021 — present}\par
\begin{itemize}
\item Full-stack web, data pipelines, scrapers, and AI integrations for Canberra Cloud Kitchen, Our Tutor, Quintet Automotive, Harin's Teas, mHits AU; co-built an AI-driven surgical scheduling tool (\href{https://team101.life}{team101.life}).
\end{itemize}

%% ---- Research --------------------------------------------------------
\edsection{Research}

{\bfseries QEM Mesh Simplification with skeletonization \& CNNs} — structure-aware mesh decimation preserving fine geometric features. \detail{2024 · \href{https://aware-mesh-simplification.web.app}{aware-mesh-simplification.web.app}}\par
\vspace{2pt}
{\bfseries Real-Time Engine Tuning via ML} — live optimisation of internal-combustion engine parameters for efficiency and emissions. \detail{2024 · \href{https://realtimeenginetuning.web.app}{realtimeenginetuning.web.app}}\par
\vspace{2pt}
{\bfseries PPO Reinforcement Learning for Equities Trading} — resource-efficient policy-gradient agent; productised as a trading-bot service. \detail{2023}

%% ---- Recognition -----------------------------------------------------
\edsection{Recognition}
PyCon AU 2021 — Speaker · Young ICT Explorers — Regional Winner (2021) · AI Hack Melbourne — 4th (2023) · Code Quest, Lockheed Martin — Runners-up (2021) · Jane Street Electronic Trading Challenge (2024) · IMC Global Trading Challenge (2025) · Australian Informatics Olympiad — Credit (2019\,–\,21)

%% ---- Stack -----------------------------------------------------------
\edsection{Stack}
\begin{tabularx}{\linewidth}{@{}lX@{}}
\monocaps{Lang}  & Python · Rust · C / C++ · Haskell · TypeScript · APL · Assembly \\
\monocaps{ML}    & PyTorch · BioCLIP · NVIDIA DALI · cuDF · Weights \& Biases · NumPy \\
\monocaps{Build} & React · Svelte · Vue · React Native · Firebase · Node · AWS · GCP · Linux · CI/CD \\
\end{tabularx}

%% ---- Education -------------------------------------------------------
\edsection{Education}
{\bfseries Australian National University} — Bachelor of Advanced Computing, Major in Machine Learning, Minor in Mathematics\dates{Jan 2022 — Jun 2026}\par
\detail{Coursework: functional programming, logic \& proofs, array programming, systems, ML. ANU Extension — Astrophysics (2021).}

\end{document}
